Survival Analysis

### 2014-03-29 presentation.Rnw
Got sample timeline up!

@@

\begin{frame}{Data Collection Issues}
<<example-timeline, echo=FALSE, fig=TRUE>>=

@
\end{frame}

>>>>

<<echo=FALSE>>=
library(ggplot2)
library(survival)
@

@@

\begin{frame}{Data Collection Issues}
<<example-timeline, echo=FALSE, fig=TRUE, width=5, height=4>>=
timeline <- read.csv('example-timeline.csv', header=TRUE, row.names=1)

ggplot(timeline) +
  xlab('time') +
  ylab('observation') +
  labs(
    colour = "Observation",
    shape = "Event Occured?")+
  geom_segment(aes(
    colour = rownames(timeline),
    x = start,
    xend = end,
    y = rownames(timeline),
    yend = rownames(timeline))) +
  geom_point(aes(
    colour = rownames(timeline),
    x = start,
    y = rownames(timeline)), size = 4, title="asdf") +
  geom_point(aes(
    colour = rownames(timeline),
    shape = event,
    x = end,
    y = rownames(timeline)), size = 4) +
  geom_vline(
    xintercept = 6,
    colour = 'red',
    linetype = 'longdash')
@
\end{frame}
